---
title: "Process_Analysis"
output:
  pdf_document: default
  html_notebook: default
---
This is R Notebook present a process analysis of 746 completed, fully validated, and archived projects in the HOT Tasking Manager (HOT-TM). Process discovery was performed using bupaR, a suite of open-source R packages for business process data analysis.
```{r}
# Import required libraries
suppressWarnings({
library(bupaverse)
library(reshape2)
library(gt)
library(scales)
library(readr)
library(dplyr)
library(magrittr)
library(ggplot2)
library(Hmisc)
library(stringr)
})
```

Read event data
The files containing project info (projects.csv) and project states(eventlog.csv) are read.
```{r}
event_log_df <- read.csv("splits_invalidations.csv", stringsAsFactors = FALSE, sep = ",")
projects <- read.csv("projects.csv", stringsAsFactors = FALSE, sep = ",")
event_log_df[c('projectId', 'task')] <- str_split_fixed(event_log_df$taskId, '_', 2)
projects$projectId <- as.character(projects$projectId)
event_log_df = merge(x = event_log_df, y = projects[,c("projectId","difficulty","priority")], by = "projectId")
event_log_df <- event_log_df %>%
  convert_timestamps(columns = c("start", "complete"), format = ymd_hms) %>%
  activitylog(case_id = "taskId", activity_id = "action", resource_id = "actionBy", timestamps = c("start", "complete"))
event_log_df <- event_log_df %>%  mutate(action_duration = difftime(as.POSIXct(`complete`), as.POSIXct(`start`), units = "mins"))
```

Project states
```{r}
head(event_log_df)
```
Project info
```{r}
head(projects)
```
Summary of the eventlog 
```{r}
summary(event_log_df)
```

Absolute frequency of states in the eventlog.
```{r}
event_log_df %>% activity_frequency("activity")
```


Activity presence shows in what percentage of cases an activity is present.
```{r}
event_log_df %>% activity_presence()
```
```{r}
tmp <- event_log_df  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```



```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```


```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
event_log_df %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
``` 

```{r}
event_log_df[event_log_df$difficulty == "EASY",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$difficulty == "EASY",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

```{r}
event_log_df[event_log_df$difficulty == "MODERATE",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$difficulty == "MODERATE",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

```{r}
event_log_df[event_log_df$difficulty == "CHALLENGING",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$difficulty == "CHALLENGING",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

```{r}
event_log_df[event_log_df$priority == "LOW",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$priority == "LOW",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces =10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

```{r}
event_log_df[event_log_df$priority == "MEDIUM",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$priority == "MEDIUM",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

```{r}
event_log_df[event_log_df$priority == "HIGH",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$priority == "HIGH",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

```{r}
event_log_df[event_log_df$priority == "URGENT",] %>% activity_presence()
```

```{r}
tmp <- event_log_df[event_log_df$priority == "URGENT",]  %>% filter_trace_frequency(percentage = 0.85)
```

```{r}
totalmapping <- tmp[tmp$action == "LOCKED_FOR_MAPPING",] %>% group_by(taskId) %>% summarise(mapping_duration = sum(action_duration)) 
totalmapping
```

```{r}
totalvalidation <- tmp[tmp$action == "LOCKED_FOR_VALIDATION",] %>% group_by(taskId) %>% summarise(validation_duration = sum(action_duration)) 
totalvalidation
```

```{r}
mappingvalidation = merge(totalmapping, totalvalidation, by='taskId', all=TRUE)
mappingvalidation[is.na(mappingvalidation)] = 0
mappingvalidation
```

```{r}
mappingvalidation <- transform(mappingvalidation, morevalidation= ifelse(mapping_duration < validation_duration, 1, 0)) 
mean(mappingvalidation$morevalidation)*100
```

```{r}
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
tmp %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

In the frequency process map, nodes represent the absolute number of activity instance executions and edges represent the absolute number of times source and target activities were executed directly following each other. To provide a clear process map, the event log was previously filter using filter_trace_frequency(). Setting percentage = 0.85 selects at least 85% of the cases, starting with those that have the highest frequency.
```{r}
tmp <- event_log_df %>% filter_trace_frequency(percentage = 0.85)
tmp %>%  process_map(frequency("absolute"))
```

trace_explorer() with coverage argument n_traces = 10 shows the 10 most frequent in the event log.
```{r}
event_log_df %>%    trace_explorer(n_traces = 10, show_labels = FALSE, coverage_labels = c("relative"))
```

In the temporal process map, the value of nodes and edges represent the median duration in days of activities and waiting times.
```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "days"))
```

```{r}
tmp1 <- tmp
tmp1 %>%  process_map(performance(median, "mins"))
```

# Organisation {#organisation}
Composition of the total number of contributors of the analysed projects according to their mapping level.

```{r}
mappingLevel <- event_log_df %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

Breakdown of status execution frequency per mapping level.

```{r}
data_pivot <- dcast(event_log_df, action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$difficulty == "EASY",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
easy <- event_log_df[event_log_df$difficulty == "EASY",]
data_pivot <- dcast(easy[easy$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(easy[easy$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$difficulty == "EASY",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$difficulty == "MODERATE",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
moderate <- event_log_df[event_log_df$difficulty == "MODERATE",]
data_pivot <- dcast(moderate[moderate$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(moderate[moderate$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$difficulty == "MODERATE",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$difficulty == "CHALLENGING",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
challenging <- event_log_df[event_log_df$difficulty == "CHALLENGING",]
data_pivot <- dcast(challenging[challenging$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(challenging[challenging$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$difficulty == "CHALLENGING",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$priority == "LOW",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
low <- event_log_df[event_log_df$priority == "LOW",]
data_pivot <- dcast(low[low$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(low[low$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$priority == "LOW",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$priority == "MEDIUM",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
medium <- event_log_df[event_log_df$priority == "MEDIUM",]
data_pivot <- dcast(medium[medium$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(medium[medium$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$priority == "MEDIUM",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$priority == "HIGH",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
high <- event_log_df[event_log_df$priority == "HIGH",]
data_pivot <- dcast(high[high$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(high[high$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$priority == "HIGH",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```

```{r}
data_pivot <- dcast(event_log_df[event_log_df$priority == "URGENT",], action ~ mappingLevel,value.var = "taskId", length)
data_pivot$sum <-  data_pivot$ADVANCED + data_pivot$BEGINNER + data_pivot$INTERMEDIATE
data_pivot$ADVANCEDper <- round(data_pivot$ADVANCED/data_pivot$sum*100,1)
data_pivot$BEGINNERper <- round(data_pivot$BEGINNER/data_pivot$sum*100,1)
data_pivot$INTERMEDIATEper <- round(data_pivot$INTERMEDIATE/data_pivot$sum*100,1)
data_pivot[c("action","ADVANCEDper","BEGINNERper","INTERMEDIATEper")] %>% gt() %>%  data_color(columns = 2:4, colors = col_numeric(palette = c("white","darkgreen"),domain = c(0,100)))
```

```{r}
urgent <- event_log_df[event_log_df$priority == "URGENT",]
data_pivot <- dcast(urgent[urgent$action %in% c('LOCKED_FOR_MAPPING','MAPPED','AUTO_UNLOCKED_FOR_MAPPING','SPLIT','BADIMAGERY'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
data_pivot <- dcast(urgent[urgent$action %in% c('LOCKED_FOR_VALIDATION','INVALIDATED','VALIDATED','AUTO_UNLOCKED_FOR_VALIDATION'),], projectId ~ mappingLevel,value.var = "username", fun.aggregate = uniqueN)
sum(data_pivot$BEGINNER)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$INTERMEDIATE)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
sum(data_pivot$ADVANCED)/(sum(data_pivot$ADVANCED)+sum(data_pivot$INTERMEDIATE)+sum(data_pivot$BEGINNER))*100
```

```{r}
mappingLevel <- event_log_df[event_log_df$priority == "URGENT",] %>%  group_by(mappingLevel) %>% summarise(count = n_distinct(actionBy))
mappingLevel$percentage <- round(mappingLevel$count/sum(mappingLevel$count)*100,1)
mappingLevel
```
